On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2021-01-30 documents/background.tex
gosh darnit
I keep re-writing things but they don't get any better!

@@

TRL 0

@@

Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped protein encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness with 120 pulses, about 500 nanoseconds each, at 3 MV/m. Electron microscopy demonstrates that the mechanism is irreversible damage to the capsid or envelope respectively and release of the core.

@@

In this observation, the thermal artifact cannot necessarily be discounted. The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids and 50 C for envelopes\cite{Stability1985}}. The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses. 
\end{autem}

@@

>>>>

\section{Background}

@@

%3 MV/m * 1000 electronCharge * 1 angstrom / (boltzmannConstant * 310 K) = 1.12 kT
From a pessimistic energetic perspective, 
, where 0.1 angstrom is derived from the lipid MD simulation. [that's not right!] Compare to ~5 $k_b T$ per protein for capsid binding \cite{Energies2012} \cite{Weak2002} and $ (\text{17 to 78 kJ/mol})  / (310 \text{ K}\ k_b) = $ 6 to 30 $k_b T$ for lipid bilayer pore formation \cite{Atomistic2014a}.
%17 or 78 kJ/mol / (boltzmannConstant * 310 K) / avogadroConstant = 6.5 to 30.3 kT

@@

Mizuno \cite{Inactivation1990} inactivate SVD Enterovirus (a 27 nm non-enveloped protein encapsidated ssRNA) and EHV (a 100 nm enveloped dsDNA) with 100\% effectiveness with 120 pulses, about 500 nanoseconds each, at 3 MV/m. Electron microscopy demonstrates that the mechanism is irreversible damage to the capsid or envelope respectively and subsequent release of the core, and is unlike thermal treatment.

@@

Though the temperature was monitored, In this observation, the thermal artifact cannot necessarily be completely discounted. The energy dissipated was sufficient to cause a significant temperature rise if localized hot-spots appeared \footnote{(43 cal/cc * (3 microliters)) / (3 milligrams * 4.2 J/(g K)) = ~50 $\Delta$C, whereas melting temperatures are typically about 90 C for capsids \cite{Thermal1999} and 50 C for envelopes\cite{Stability1985}}. \\ The electrodes were not insulated, so electrochemical effects are possible but unlikely given the short duration of the pulses. 
\end{autem}

@@

Electrorotation large field but not seen.

### 2021-01-30 documents/lessons_learned.tex
Apparent success?
I keep re-writing things but they don't get any better!

@@

@@

It is useful to first strictly implement precisely as written, and only when all parts are operational and understood, begin modifying for your own use.

>>>>

There is something of an over-arching lesson learned - maybe it's not actually good to learn this lesson, maybe it's more useful to assume, but...

@@

We have seen time and again that investment in science and technology - even basic research, so distant from the mechanics of society - can produce outsized effects on quality-of-life. Both NASA and CERN, neither of which do much related to people, produce a 7-to-1 and 3-to-1 return on investment.

All of which will be a great comfort to the dead.

You could fit a pandemic through a good-sized breakthrough. The vaccines are an excellent example, really. Moreover you learn more to be more useful in the future. Phage display  -

So what went wrong here?

Is it the avenue of investigation? Perhaps a lack of peer input. Maybe there were too few people involved - now that science is "bigger", we need bigger groups to efficiently manage it?

Maybe if you don't have sufficient resources (knowledge, equipment, peers) to persue something efficiently, maybe it's not worth you pursuing it at all.

If a well-stocked lab and a few specialists could have banged this out in a week (which they could), was it worth it to bang this out in a year? Did anything actually go wrong, or is this just how it works?

It's interesting thoughts to toy with, but probably not a great idea to get wrapped up in this sort of self-pity and melancholic thinking. Or maybe it is. Who knows.

Doing the same thing that I was doing before - sitting in a basement, working on electronics. What are the odds that the thing that I was doing before was the right thing to do against a virus?

When to publish

One the one hand, there're some pretty good reasons to want embargoes, like the Ingelfinger rules - no need to lather up a furor just for some idle musings, and publishing too early is a terrible idea. In retrospect, it was extremely good that I did not make a fuss about some extremely positive data; it turned out to be an embarrassing mistake in

On the other hand, embargo rules came from publishers, and (like ) these decisions were probably somewhat motivated by financial considerations.

There's a recent movement towards more "live" and open science - it's hard to tell when the, especially in a pandemic. Fortunately, it's not like any of what we're discussing here actually matters, anyways.

@@

It is useful to first strictly implement a method precisely as written, and only when all parts are operational and understood, begin modifying for your own use.

### 2021-01-30 documents/molecular_dynamics.tex
still broken sources
More discussion
Building the thing
I keep re-writing things but they don't get any better!

An illustrative - to ensure that there was nothing egregiously wrong with the Stokes drag calculation and to extract various. Certainly this has been done dozens of times in the past. For other reasons to play around with. ]\

\begin{figure}[H]
%	\makebox[\textwidth][c]{
	\centering
	\subfloat[Flower one.]{
	\includegraphics[width=0.4\textwidth]{Vescicle.png}

@@

These results are not in any way quantitative, nor do they truly suggest that the effect exists. Lipid vesicle simulations with MARTINI force fields have yielded large-scale stiffness values which are orders of magnitude\cite{Determining2014} from those found experimentally; the speed of sound is also.

@@

@@

\printbibliography{}

>>>>

An illustrative - to ensure that there was nothing egregiously wrong with the Stokes drag calculation and to extract rotational friction coefficients. Certainly equivalent simulations have been done dozens of times in the past.

\begin{figure}[H]
%	\makebox[\textwidth][c]{
	\centering
	\subfloat[Flower one.]{
	\includegraphics[width=0.4\textwidth]{vescicleds.png}

@@

These results are not in any way quantitative, nor do they truly suggest that the effect exists. Critical issues include the lack of deconvolution from the input impulse bandwidth. Lipid vesicle simulations with MARTINI force fields have yielded large-scale stiffness values which are orders of magnitude\cite{Determining2014} from those found experimentally; the speed of sound is also.

@@

the intitial transient must be deconvolved

@@

Interestingly, finite-element analysis appears to be a perfectly sensible approach to coarse-graining, just like might be done with a macro-scale structure.

### 2021-01-30 documents/paper.tex
gosh darnit
I keep re-writing things but they don't get any better!

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{pulse_exposure_setup.JPG}
	\caption{\\ Pulse exposure jig. Autosampler Pulse shaper not shown. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
	\caption{\\ The misguided {\it Eppenwolf} pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
\end{figure}

@@

The mechanism restricts the possible modes of application; it would be useful to

\paragraph{\textbf{Personal 'electromagnetic mask'}}\

Even with judicious use of phased-arrays, spatial power-combining, etc, each transistor can only reasonably maintain sterility in approx. $ 0.1 \text{ m}^3 $.

\paragraph{\textbf{Direct treatments at the fundamental}}\

\paragraph{\textbf{More fanciful concepts}}\

Many systems operate in these X-band frequency ranges; and precision

It is easy to produce megawatts of power at these frequency ranges using Klystrons. Assuming an appropriate antenna, a single 50MW SLAC XL-class klystron with a PRF of 180 Hz could sanitize almost a square kilometer every second. \footnote{Giving 'asceptic field' new meaning.}

On the other hand, if this is conducted in outdoor free-space, sunlight

Existing marine, weather, and aviation radar systems often use the X-band; depending on the focusing power

\paragraph{Sensing}

there is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019]. Such scholarly silence is usually an indicator that a technique is impossible for reasons so obvious they scarcely bear repeating.

However, [Oberoi 2012] find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.

Of course, discriminating miniscule returns in free-space is not easy; but with precise knowledge of this resonance mode, it may become somewhat easier. Frequency-domain measurements can be made with incredible precision; and there are many parameters by which virions could be discriminated; ring-up time of the resonance, excitation non-linearity, etc.

@@

@@

@@

>>>>

\begin{table}[h!]
	\centering
	\begin{tabular}{ |c|c|c|c| } 
		\hline
		col1 & col2 & col3 \\
		\hline
		& cell2 & cell3 \\ 
		& cell5 & cell6 \\ 
		& Negative & 5 \\ 
		\hline
	\end{tabular}

	\caption{Data from testing on bacteriophage. Data rounded to the nearest thousand photon counts. Not thoroughly characterized. Repeatability between test conditions   Background was no. 
	The flurometer printed a constant stream of the integration, all within the random error between capture windows $\sigma=0.5$ kcounts. }
\end{table}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{pulse_exposure_setup.JPG}
	\caption{\\ \textit{Chengxiang} pulse exposure jig. pulser seen off the left. Autosampler Pulse shaping plate not shown. Aluminum disc belongs to the scan-conversion digitizer, not used in this study.}
\end{figure}

\begin{figure}[H]
	\captionsetup{singlelinecheck = false, justification=justified}
	\centering
	\includegraphics[width=\textwidth]{eppenwolf_2.jpg}
	\caption{\\ \textit{Eppenwolf} misguided pulsed X-Band microwave spectrometer used in this study, pictured with the near-field cuvette installed.}
\end{figure}

@@

\section{Sensing}

There is little discussion on microwave virus detection, with the notable exception of [Mehrotra 2019].

However, \cite{Microwave2012} find that - in controlled conditions - they can detect a single E. Coli bacterium in 50 uL of broth via a microwave cavity.

Havelka \cite{Highfrequency2011} discuss microtubules.

With an extremely high power excitation pulse, the problem may become somewhat easier; especially if the virus has a ring-down that can be subjected to autocorrelation.

However, the dipole radiation power expected in even the most implausibly optimistic case would be about as follows:

$$P={\frac {\mu _{0}(2 \pi \cdot 20 GHz) ^{4}(0.5 \text{nm} * 10^6 e^-)^{2}}{12\pi c}} = 7.1 \times10^{-16} \text{W} $$

which for most reasonable conditions would $\approx 0.5 Janskies$, meaning that the power radiated from the virus would be considerably overpowered by the milky way.

% (magneticConstant*(2 pi * 20 GHz)^4 * (0.1 nm * 1000 * electronCharge)^2)/(12*pi * c) -> W

@@

\section{Appendix on microwave design}

@@

\section{Appendix on microbiology}

@@

\subfile{lessons_learned}
